Massimiliano Di Penta is associate professor at the University of Sannio, Italy since December 2011. Before that, he was assistant professor in the same University since December 2004. His research interests include software maintenance and evolution, mining software repositories, empirical software engineering, search-based software engineering, and service-centric software engineering. He is author of over 200 papers appeared in international journals, conferences and workshops. He serves and has served in the organizing and program committees of over 100 conferences such as ICSE, FSE, ASE, ICSM, ICPC, GECCO, MSR WCRE, and others. He has been general co-chair of various events, including the 10th IEEE Working Conference on Source Code Analysis and Manipulation (SCAM 2010), the 2nd International Symposium on Search-Based Software Engineering (SSBSE 2010), and the 15th Working Conference on Reverse Engineering (WCRE 2008). Also, he has been program chair of events such as the 28th IEEE International Conference on Software Maintenance (ICSM 2012), the 21st IEEE International Conference on Program Comprehension (ICPC 2013), the 9th and 10th Working Conference on Mining Software Repository (MSR 2013 and 2012), the 13th and 14th Working Conference on Reverse Engineering (WCRE 2006 and 2007), the 1st International Symposium on Search-Based Software Engineering (SSBSE 2009), and other workshops. He is currently member of the steering committee of ICSME, MSR, SSBSE, and PROMISE. Previously, he has been steering committee member of other conferences, including ICPC, SCAM, and WCRE. He is in the editorial board of IEEE Transactions on Software Engineering, the Empirical Software Engineering Journal edited by Springer, and of the Journal of Software: Evolution and Processes edited by Wiley.